### 2022-08-08 README.Rmd
getting release-ready

<!-- badges: start -->
[![R-CMD-check](https://github.com/zabore/ppseq/workflows/R-CMD-check/badge.svg)](https://github.com/zabore/ppseq/actions)
[![Codecov test coverage](https://codecov.io/gh/zabore/ppseq/branch/main/graph/badge.svg)](https://codecov.io/gh/zabore/ppseq?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/zabore/ppseq/workflows/R-CMD-check/badge.svg)](https://github.com/zabore/ppseq/actions)
[![Codecov test coverage](https://codecov.io/gh/zabore/ppseq/branch/main/graph/badge.svg)](https://app.codecov.io/gh/zabore/ppseq?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->
